### 2008-03-17 SAiP/Module1/H3/doc/qualityattributes.tex
Adding lable
Quality attribute scenario refinement tables added.

The scenarios may be further clarified in order to include the aspects of availability and performance, as shown below.

\begin{quote}
The customer browses the beer catalogue for descriptions and reviews and receives the result within 5 seconds 99\% of the time, 30 seconds 0,9\% of the time and more than 30 seconds 0,1\% of the time.

The customer selects appropriate beers for purchase and these are added to his shopping basket. When the customer checks out, payment is validated through the payment service within 30 seconds.
\end{quote}

\fixme{Answer question 2.2}

\subsection{Quality Attributes - Question 3}

>>>>

The scenarios may be further clarified in order to include the aspects of availability and performance, as shown in tables \ref{tab:availability} and \ref{tab:performance} below:

\begin{table}[H]
\begin{center}
\begin{tabular}{|p{0.3cm}|p{2.5cm}|p{8cm}|}
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Scenario(s):} & The customer browses the beer catalogue for descriptions and reviews and receives a timely response \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Relevant Quality Attributes:} & Availability, (Performance) \\
  \hline
  \multirow{6}{*}{\begin{sideways}{\bfseries Scenario Parts}\end{sideways}}
  & {\bfseries Source:} & The user \\
  \cline{2-3}
  & {\bfseries Stimulus:} & Browsing the beer catalogue \\
  \cline{2-3}
  & {\bfseries Artifact} & The system \\
  \cline{2-3}
  & {\bfseries Environment:} & During normal operation \\
  \cline{2-3}
  & {\bfseries Response:} & Web page presented to user \\
  \cline{2-3}
  & {\bfseries Response Measure:} & The result is presented within 5 seconds 99\% of the time, 30 seconds 0,9\% of the time and more than 30 seconds 0,1\% of the time \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Questions:} & \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Issues:} & The response measure is also dependent on the speed of the users internet connection and computer hardware. \\
  \hline
\end{tabular}
\caption{Availability scenario for the Beer Web Store}
\label{tab:availability}
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|p{0.3cm}|p{2.5cm}|p{8cm}|}
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Scenario(s):} & When the customer checks out, payment is validated through the payment service within 30 seconds. \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Relevant Quality Attributes:} & Performance, (Availability) \\
  \hline
  \multirow{6}{*}{\begin{sideways}{\bfseries Scenario Parts}\end{sideways}}
  & {\bfseries Source:} & The user \\
  \cline{2-3}
  & {\bfseries Stimulus:} & The customer checks out \\
  \cline{2-3}
  & {\bfseries Artifact} & The system \\
  \cline{2-3}
  & {\bfseries Environment:} & During normal operation \\
  \cline{2-3}
  & {\bfseries Response:} & Result of payment validation if presented to the user \\
  \cline{2-3}
  & {\bfseries Response Measure:} & Payment is validated through the payment service within 30 seconds \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Questions:} & \\
  \hline
  \multicolumn{2}{|p{3cm}|}{\bfseries Issues:} & The response measure is also dependent on the performance of the payment service. \\
  \hline
\end{tabular}
\caption{Performance scenario for the Beer Web Store}
\label{tab:performance}
\end{center}
\end{table}

\fixme{Answer question 3.2}

\subsection{Quality Attributes - Question 3}
\label{sec:qa_q3}
